Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-22 Moltres.tex
more details on export control

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{github_build_2017} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. While export control laws have the potential 
to restrict openness of software that is dual use, Moltres requires that 
cross sections be provided by the user, is tailored to molten salt reactor 
physics, and joins a veritable parade of open academic nuclear engineering
software such as OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
PyNE\cite{bates_pyne_2014,biondo_quality_2014}.

>>>>

Moltres is an open source code licensed under \gls{LGPL} terms so the 
\gls{MSR} community can freely use, interrogate, and improve it.  Its openness 
is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{github_build_2017} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. While export control laws have the potential 
to restrict openness of neutron transport software that is dual use, there is 
no reason to believe that Moltres could be used for weapons proliferation. 
Moltres requires that cross sections be provided by the user, implements a 
combination of algorithms that can be easily derived from open literature, is 
tailored to molten salt reactor physics. Accordingly, Moltres joins a veritable 
parade of open academic nuclear engineering software such as 
OpenMC\cite{romano_openmc:_2015}, OpenMOC\cite{boyd_openmoc_2014}, and 
PyNE\cite{bates_pyne_2014,biondo_quality_2014}.
